Time and space specifications for stencils

### 2016-03-10 paper.tex
corrected type of relative indices

@@

\begin{figure}
\begin{align*}
\hspace{-2em}
\begin{array}{c}
\hspace{-1em}
\setlength{\arraycolsep}{0.1em}
\begin{array}{rl}
\interp{\textit{spec}; \textit{specs}} & = \interp{spec} \cup
  \interp{\textit{specs}} \\
%% TEMPORAL SPECS
% \interp{\texttt{v} : \texttt{forward} \; \texttt{depth}=n\texttt{\{u\}} \;
%  \texttt{dims=t}} & =  \{ (\texttt{u}, \textit{ix})^m \mid \forall m,
%                     ix : \mathbb{Z}^{\mathbb{D}}, \textit{ix} \,
%                     \texttt{t} = 0 \} \\[0.4em]
%% SPATIAL SPECS
\interp{\texttt{v} : S} & = \{(\texttt{v}, ix)^m \mid ix^m \in
  \interp{S}\} \\
\end{array}\\[1em]
%\framebox{$\interp{S}$} \\[1em]
\begin{array}{ll}
& \interp{\texttt{reflexive}}
  = \\
& \hspace{0.9em}  \{ ix^m \mid \forall m, \, ix : \mathbb{Z}^{\mathbb{D}}, d : \mathbb{D}
  \, . \, d \in \textit{ds} \Rightarrow ix \, d = 0 \} \\[0.4em]
& \interp{\texttt{forward} \;\; \texttt{depth}=n \;\;
  \texttt{dims}=\textit{ds}}  = \;\; (\texttt{t} \not\in ds) \\
& \hspace{0.9em}  \{ ix^m \mid \forall m, \, ix : \mathbb{Z}^{\mathbb{D}}, d : \mathbb{D}
  \, . \, d \in \textit{ds} \Rightarrow 0 \leq (ix \, d) \leq n \} \\[0.4em]
& \interp{\texttt{backward} \;\; \texttt{depth}=n \;\; \texttt{dims}=\textit{ds}}
  = \; \; (\texttt{t} \not\in ds) \\
& \hspace{0.9em}  \{ ix^m \mid \forall m, \, ix : \mathbb{Z}^{\mathbb{D}}, d : \mathbb{D}
  \, . \, d \in \textit{ds} \Rightarrow (-n) \leq (ix \, d) \leq 0 \}
  \\[0.4em]
& \interp{\texttt{read-once} \; S} = \{ ix^1 \mid ix^m \in \interp{S}
  \} 
\end{array}
\end{array}
\end{align*}
\textit{$a^m \in A$ means there are $n$ copies of $a$ in
  the multi-set $A$}
\caption{Multi-set model of specifications}
\label{fig:model}
\end{figure}

@@

\paragraph{Proof}
\begin{itemize}
\item \textsc{coalesceF}
\begin{align*}
\llbracket & \texttt{v} : \texttt{fwd} \; \texttt{dims}=ds \; \texttt{depth}=n; \,
  \texttt{v} :  \texttt{fwd} \; \texttt{dims}=ds \;
  \texttt{depth}=n+1)\rrbracket \\
& =  \{ (\texttt{v}, ix)^m \mid \forall \, m, ix : \mathbb{Z}^{\mathbb{N}}, d : \mathbb{N}
  \, . \, d \in \textit{ds} \Rightarrow ix \, d \leq (n+1) \} \; \cup \; \{ ix^m \mid \forall \, m, ix : \mathbb{Z}^{\mathbb{N}}, d : \mathbb{N}
  \, . \, d \in \textit{ds} \Rightarrow ix \, d \leq n \}\\
& =  \{ (\texttt{v}, ix)^m \mid \forall \, m, ix : \mathbb{Z}^{\mathbb{N}}, d : \mathbb{N}
  \, . \, d \in \textit{ds} \Rightarrow ((ix \, d \leq (n+1)) \vee (ix \,
  d \leq n)) \} \\
& =  \{ (\texttt{v}, ix)^m \mid \forall \, m, ix : \mathbb{Z}^{\mathbb{N}}, d : \mathbb{N}
  \, . \, d \in \textit{ds} \Rightarrow ix \, d \leq (n+1) \} \\
& = \interp{\texttt{v} : \texttt{fwd} \; \texttt{dims}=ds \;
  \texttt{depth}=n + 1} \qquad \Box
\end{align*}
\end{itemize}

>>>>

\newcommand{\relix}{(\mathbb{Z}_\bot)^\mathbb{D}}

@@

\begin{figure}
\begin{align*}
\hspace{-2em}
\begin{array}{c}
\hspace{-1em}
\setlength{\arraycolsep}{0.1em}
\begin{array}{rl}
\interp{\textit{spec}; \textit{specs}} & = \interp{spec} \cup
  \interp{\textit{specs}} \\
%% TEMPORAL SPECS
% \interp{\texttt{v} : \texttt{forward} \; \texttt{depth}=n\texttt{\{u\}} \;
%  \texttt{dims=t}} & =  \{ (\texttt{u}, \textit{ix})^m \mid \forall m,
%                     ix : \mathbb{Z}^{\mathbb{D}}, \textit{ix} \,
%                     \texttt{t} = 0 \} \\[0.4em]
%% SPATIAL SPECS
\interp{\texttt{v} : S} & = \{(\texttt{v}, ix)^m \mid ix^m \in
  \interp{S}\} \\
\end{array}\\[1em]
%\framebox{$\interp{S}$} \\[1em]
\begin{array}{ll}
& \interp{\texttt{reflexive}}
  = \\
& \hspace{0.9em}  \{ ix^m \mid \forall m, \, ix : \relix, d : \mathbb{D}
  \, . \, d \in \textit{ds} \Rightarrow ix \, d = 0 \} \\[0.4em]
& \interp{\texttt{forward} \;\; \texttt{depth}=n \;\;
  \texttt{dims}=\textit{ds}}  = \;\; (\texttt{t} \not\in ds) \\
& \hspace{0.9em}  \{ ix^m \mid \forall m, \, ix : \relix, d : \mathbb{D}
  \, . \, d \in \textit{ds} \Rightarrow 0 \leq (ix \, d) \leq n \} \\[0.4em]
& \interp{\texttt{backward} \;\; \texttt{depth}=n \;\; \texttt{dims}=\textit{ds}}
  = \; \; (\texttt{t} \not\in ds) \\
& \hspace{0.9em}  \{ ix^m \mid \forall m, \, ix : \relix, d : \mathbb{D}
  \, . \, d \in \textit{ds} \Rightarrow (-n) \leq (ix \, d) \leq 0 \}
  \\[0.4em]
& \interp{\texttt{read-once} \; S} = \{ ix^1 \mid ix^m \in \interp{S}
  \} 
\end{array}
\end{array}
\end{align*}
\textit{$a^m \in A$ means there are $n$ copies of $a$ in
  the multi-set $A$}
\caption{Multi-set model of specifications}
\label{fig:model}
\end{figure}

@@

\paragraph{Proof}
\begin{itemize}
\item \textsc{coalesceF}
\begin{align*}
\llbracket & \texttt{v} : \texttt{fwd} \; \texttt{dims}=ds \; \texttt{depth}=n; \,
  \texttt{v} :  \texttt{fwd} \; \texttt{dims}=ds \;
  \texttt{depth}=n+1)\rrbracket \\
& =  \{ (\texttt{v}, ix)^m \mid \forall \, m, ix : \relix, d : \mathbb{N}
  \, . \, d \in \textit{ds} \Rightarrow ix \, d \leq (n+1) \} \; \cup \; \{ ix^m \mid \forall \, m, ix : \mathbb{Z}^{\mathbb{N}}, d : \mathbb{N}
  \, . \, d \in \textit{ds} \Rightarrow ix \, d \leq n \}\\
& =  \{ (\texttt{v}, ix)^m \mid \forall \, m, ix : \relix, d : \mathbb{N}
  \, . \, d \in \textit{ds} \Rightarrow ((ix \, d \leq (n+1)) \vee (ix \,
  d \leq n)) \} \\
& =  \{ (\texttt{v}, ix)^m \mid \forall \, m, ix : \relix, d : \mathbb{N}
  \, . \, d \in \textit{ds} \Rightarrow ix \, d \leq (n+1) \} \\
& = \interp{\texttt{v} : \texttt{fwd} \; \texttt{dims}=ds \;
  \texttt{depth}=n + 1} \qquad \Box
\end{align*}
\end{itemize}
